\input{header}
\begin{document}
\fontfamily{phv}\selectfont

\begin{center}
{\bf \LARGE Electromagnetic Field 2018}\\[12pt]
{\Large Sponsorship Agreement}
\end{center}

This Sponsorship Agreement is entered into as of the last signature date below (the ``Effective Date''), between:
\begin{itemize}
    \item Electromagnetic Field Ltd.\ of 2 Ockendon Mews, London N1 3JL, UK (``EMF''), and
    \item <<sponsor name and address>> (the ``Sponsor'')
\end{itemize}

for the purposes of supporting Electromagnetic Field 2018 (the ``Event''), held on August 31st-September 2nd, 2018.

\begin{enumerate}

\subsection*{Grant of Rights}

\item EMF grants the Sponsor the sponsorship rights set out in the attached Schedule,
during the Sponsorship Period.

\item The Sponsor grants and EMF accepts a worldwide, non-exclusive, royalty free,
sub-licensable license to use the Sponsor's Marks:
\begin{enumerate}
    \item during the Sponsorship Period for the delivery of the Sponsorship Rights;
    \item in perpetuity to promote and exploit the Event in any media.
\end{enumerate}

\item If the sponsorship rights include logo placement on, or other benefits relating to the TiLDA
electronic badge:
\begin{enumerate}
    \item the Sponsor acknowledges that the design and manufacture of the badge is carried out
            by volunteers and sponsors and is subject to significant risks.
    \item EMF will make best efforts to ensure that the badge is fully functional and is
            distributed to attendees during the Event. If this is not possible, EMF
            will arrange for the badges to be distributed after the Event.
    \item the Sponsor will not be entitled to any refund of the Sponsorship Fee, either partial
            or in full, if there are delays in distribution of the badge or if the badge is
            limited in functionality.
\end{enumerate}

\item The Sponsor will be responsible for promptly providing EMF with a digital logo in vector
    (PDF, EPS, or SVG) or high quality raster (PNG or TIFF of at least 600dpi) format (the "assets"),
        for inclusion in marketing material.
        EMF will not be liable for failing to deliver sponsorship benefits due to
        the Sponsor's failure to provide appropriate assets.
\item The name and email address of all recipients of complimentary tickets must be notified by the Sponsor 
        to EMF by 12pm on Friday August 17th, 2018, or the tickets will be forfeit.
\item If the sponsorship rights include the right to display banners, posters, or other printed
        material at the event, the Sponsor is responsible for supplying these items.

\subsection*{Term}

\item The Sponsorship Period will start at the date of this Agreement and will continue up to
2 weeks after the last day of the Event.

\subsection*{Fee}

\item In consideration of the sponsorship rights granted to the Sponsor, the Sponsor shall
pay EMF the fee and/or in-kind goods or services as set out in the attached Schedule.

%\item The Sponsorship Fee shall be due in full on return of this signed contract.

\item The Sponsorship Fee shall be payable in two instalments:
\begin{enumerate}
    \item 50\% due on return of this signed contract,
    \item 50\% due on or before Friday August 17th, 2018.
\end{enumerate}

\subsection*{In-Kind Sponsorship}

\item If the Sponsor is an EU entity and is providing goods and/or services in return for the
      Sponsorship Rights:
\begin{enumerate}
      \item the Sponsor accepts that they are undertaking a taxable supply in accordance with
      \href{https://www.gov.uk/government/publications/vat-notice-70141-sponsorship/vat-notice-70141-sponsorship}{HMRC VAT Notice 701/41},
      \item the Sponsor agrees to issue the Organiser a VAT invoice for the value of the
            goods/services provided under this agreement,
      \item EMF agrees to issue the Sponsor a VAT invoice for the value of the sponsorship.
\end{enumerate}

\subsection*{Termination}

\item EMF shall be entitled to cancel the Event and/or terminate this Agreement at any
time for any reason.
\item In the event that EMF terminates this Agreement for any reason other than the Sponsor's
breach, EMF shall refund any fees received from the Sponsor, and at the Sponsor's expense,
return any materials, and equipment, hardware and/or software loaned by Sponsor for the Event.

\subsection*{Miscellaneous}

\item The Sponsor will ensure that all of its representatives abide by the EMF
        \href{https://www.emfcamp.org/code-of-conduct}{Code of Conduct} at all times while on site.

\item This Agreement represents the entire agreement between the parties in relation to the subject
        matter of this Agreement and supersedes any previous agreement, whether written or oral,
        between the parties in relation to that subject matter.
\item This Agreement shall be governed and interpreted in accordance with the laws of England and Wales.

\end{enumerate}


\subsection*{Signed}
The parties have executed this Agreement as of the date set out below:

\SignatureAndDate{On behalf of the Organiser}

\SignatureAndDate{On behalf of the Sponsor}

\newpage

\input{sponsorship-schedule-bronze}

\end{document}

