\input{header}
\begin{document}
\fontfamily{phv}\selectfont

\begin{center}
{\bf \LARGE Electromagnetic Field 2016}\\[12pt]
{\Large Vendor Contract}
\end{center}

This Vendor Contract is entered into as of the last signature date below (the ``Effective Date''), between:
\begin{itemize}
    \item Electromagnetic Field Ltd.\ of 2 Ockendon Mews, London N1 3JL, UK (the ``Organiser''), and
    \item <company name and address> (the ``Vendor'')
\end{itemize}

for the purposes of trading at Electromagnetic Field 2016 (the ``Event''), held on August 5th-7th, 2016.

\begin{enumerate}

\subsection*{Payment}
\item The vendor agrees to pay the Organiser the sum of £500 + VAT, which will be due in
      full on return of this signed contract.
\item If the Vendor fails to comply with this contract, or does not attend the Event,
        they shall not be entitled to any refund.
\item No refunds will be given to Vendors as a result of bad weather, cancellation on the
        grounds of war or terrorism, cancellation at the request of the police or government,
        a change of programme, or necessary re-siting of stalls.
\item The Organiser will not accept responsibility for the level of trading during the event.

\subsection*{Set-up and trading times}
\item Access to the site for set-up is allowed from 12:00-20:00 on Thursday August 4th, and
        08:00-10:00 on Friday 5th.
\item Unless agreed otherwise, vendors are expected to remain open during core trading
        hours of 11:00-20:00 on Friday, Saturday, and Sunday.
\item Food vendors are encouraged to remain open later. The Event is licensed for late
        night refreshment until 02:00.
\item All vendors must be off site by 21:00 on Monday August 8th.

\subsection*{Compliance}
\item The Vendor must provide the Organiser with copies of the following documentation no later
        than Friday June 24th, 2016:
\begin{enumerate}
    \item Employers Liability and Public Liability Insurance certificate.
            Public Liability insurance must be for a minimum of £5,000,000.
    \item Local Authority Food Hygiene Certificate.
\end{enumerate}

\subsection*{Vehicles}
\item All vehicles brought on site are at the risk of the Vendor, and must be suitably insured.
        The Organiser cannot take responsibility for any loss or damage that may occur.
\item The speed limit on site is 5 miles per hour.
\item Vehicle movements on site are not permitted between the hours of 10:00 and 00:00 on
      Friday, Saturday, and Sunday, without express permission of the Organiser who will provide
      a marshall.

\subsection*{Passes}
\item The Vendor must notify the Organiser no later than Friday July 22nd with the names of
        all staff who will be attending the Event, and the registration number of all vehicles.
\item Vehicle passes will be issued and must be displayed at all times.

\subsection*{Utilites}
\item A 16A single-phase CEEform electrical connection will be provided free of charge. Larger
        connections are available on request, but may incur a fee.
\item Vendors are not permitted to bring generators on site.
\item Water will be available from a standpipe, and wastewater must be disposed of in a way
        agreed with the Organiser.

\subsection*{Restrictions}
\item Amplified music is not permitted on any stalls without written permission from the Organiser.
\item No animals are allowed on site. Any animal found will be removed and the Vendor will
        cover the cost.
\item Vendors are not permitted to sell alcohol.
\item Due to restrictions imposed by the site, the Vendor is not permitted to sell ice cream.

\subsection*{Miscellaneous}
\item The Vendor will ensure that all of its representatives abide by the EMF
        \href{https://www.emfcamp.org/code-of-conduct}{Code of Conduct} at all times while on site.
\item Before arrival on site, all communication with the Organiser should be by email sent to
        \href{mailto:vendors@emfcamp.org}{vendors@emfcamp.org}. On site, communication should be
        with the vendors coordinator or duty site manager.

\end{enumerate}

\subsection*{Signed}
The parties have executed this Agreement as of the date set out below:

\SignatureAndDate{On behalf of the Organiser}

\SignatureAndDate{On behalf of the Vendor}

\end{document}
